---
title: "Task 4: Projected Land Use"
author: "Marie Bouffard"
date: "11/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
# Attach packages
library(tidyverse)
library(readxl)
library(janitor)
library(here)
library(kableExtra)
library(stringr)
library(patchwork)

# Read in Projected LU data (2025 to 2055 Change Sheet)
LU_change_raw <- read_excel(here("Data", "4_MD_LU_2025_2055.xlsx"), sheet = 3) %>% 
  mutate(County = str_to_title(County))

# Updated Projected LU data (2025 to 2055 Change Sheet)
lu_change_update <- read_excel(here("Data", "4_MD_Tech_Study_cz_2021_20210929.xlsx"), sheet = 3) %>% 
  clean_names() %>% 
  mutate(cntyname = str_to_title(cntyname)) # change counties from all caps to sentence case

# Read in zoning data and make title case
zoning_raw <- read.csv(here("Data", "4_GenZoning_LC_Forest_Change.csv")) %>%
  clean_names() %>% 
  rename(genzone = i_genzone) %>% 
  mutate(genzone = str_to_title(genzone))

# Read in sewer data
sewer_service <- read.csv(here("Data", "4_SewerService.csv")) %>% 
  clean_names() %>% 
  mutate(genz_swr = str_to_title(genz_swr))

# Set blanks to NA
sewer_service[sewer_service == c(" ", "")] <- NA

# Land Use Pallette
lc_pallette <- c("#B0A4CC", # Light purple
                 "#8F7CB6", # Medium purple
                 "#665191", # Dark Purple
                 "#41335B", # Darkest Purple 
                 "#F6833C", # Light Orange
                 "#E45D0B", # Medium Orange
                 "#C35009", # Dark Orange
                 "#02c39a", # Teal
                 "#046865", # Dark Teal
                 "#E1BC29", # Dark Yellow
                 "#FFEE88") # Light Yellow

lu_pallette <- c("#F9DB6D", # Barren, light yellow
                 "#D9682A", # Buildings, brick
                 "#F08701", # Impervious, orange 
                 "#8DBE87", # Low veg, light green
                 "#F9A620", # Roads, light orange
                 "#57AF94", # Shrub, green-blue
                 "#6eb663", # Tree Canopy, light green
                 "#4059AD", # Water, royal blue
                 "#21A0A0") # Wetland, Blue-green

# Zoning Palette
zone_palette <- c("#5cb652", # Cropland, light green
                 "#24693d", # Forest, Dark Green
                 "#F9A620", # Impervious roads, light orange
                 "#F08701", # Impervious non-roads, dark orange 
                 "#585191", # Mixed Open, dark purple
                 "#97CC04", # Pasture, light green
                 "#E4572E", # Tree Canopy over impervious, red-orange
                 "#62466B", # Tree Canopy over turf grass, dark purple
                 "#9A7AA0", # Turf Grass, light purple
                 "#5ADBFF", # Wetlands Other, light blue
                 "#21A0A0") # Wetlands floodplain, teal

# County Pallet
county_pallette <- c("#68affc", "#485172", "#d6a7f0", "#7c46a0", "#20d8fd", "#155126", "#a2e84f", "#528f7a", "#7dd9a0", "#39970e", "#d0d9ae", "#e27040", "#f29180", "#e13224", "#922d4c", "#d9c937", "#fa217f", "#36f459", "#b825af", "#f27ff5", "#fda547", "#b7358d", "#a1e8af", "#7e52a0")

# Use stringr::str_wrap() to create breaks in long facet titles
stwr <- function(string, nwrap = 20){
  paste(strwrap(string, width = nwrap), collapse = "\n")
}

stwr = Vectorize(stwr)

```

### New Projected Land Use change
```{r}
#---------------------------------------
# Updated projected land use by land use type and county
#---------------------------------------
lu_update <- lu_change_update %>% 
  pivot_longer(!fips:cntyname, names_to = "land_use", values_to = "acres") %>% 
    mutate(full_name = case_when(
    land_use == "ir_chg" ~ "Impervious Roads",
    land_use == "inr_chg" ~ "Impervious Non-Roads",
    land_use == "tci_chg" ~ "Tree Canopy Over Impervious",
    land_use == "tg_chg" ~ "Turf Grass",
    land_use == "tct_chg" ~ "Tree Canopy over Turf Grass",
    land_use == "fore_chg" ~ "Forest",
    land_use == "wlo_chg" ~ "Wetlands (Other)",
    land_use == "wlf_chg" ~ "Wetlands (Floodplain)",
#    land_use == "wlt_chg" ~ "Wetlands (Tidal)", 
#    land_use == "wat_chg" ~ "Water", # Model not run for water and wetland
    land_use == "mo_chg" ~ "Mixed Open",
    land_use == "crp_chg" ~ "Cropland",
    land_use == "pas_chg" ~ "Pasture",
  )) %>% 
  drop_na()

# Use string wrap function
lu_update$full_name = stwr(lu_update$full_name)

# Plot
#---------------------------------------
lu_update_plot <- ggplot(lu_update, aes(x = fct_rev(cntyname), y = acres)) +
  geom_col(aes(fill = cntyname)) +
  scale_fill_manual(values = county_pallette) +
  facet_wrap(~full_name, scales = "free_y") +
  labs(x = "County", y = "Change in Area (Acres)") +
  theme_minimal() +
   geom_hline(aes(yintercept=0)) +
  theme(
    text = element_text(family = "Times"),
    strip.background = element_rect(color = "grey40", fill = "grey30"),
    strip.text = element_text(color = "white", face = "bold"),
    panel.border = element_rect(color = "grey40", fill = NA),
#    legend.position = "none",
   legend.title = element_text(size = 14, face = "bold"),
   legend.position = "bottom",
   legend.title.align = 0.5,
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text.x = element_blank(),
    axis.title.x = element_blank()) +
  guides(fill = guide_legend(title = "Jurisdiction", 
                             title.position = "top",
                             nrow = 4))

lu_update_plot

ggsave(here("Graphics", "4_lu_update_legend.jpg"), lu_update_plot, width = 8.5, height = 7)

```

Projected Land Use Faceted by County
```{r}

# Use string wrap function
lu_update$full_name = stwr(lu_update$full_name)

lu_county_plot <- ggplot(lu_update, aes(x = full_name, y = acres)) +
  geom_col(aes(fill = full_name)) +
  scale_fill_manual(values = zone_palette) +
  facet_wrap(~cntyname, scales = "free_y") +
  labs(x = "Land Use", y = "Change in Area (Acres)") +
  theme_minimal() +
   geom_hline(aes(yintercept=0)) +
  theme(
    text = element_text(family = "Times"),
    strip.background = element_rect(color = "grey40", fill = "grey30"),
    strip.text = element_text(color = "white", face = "bold"),
    panel.border = element_rect(color = "grey40", fill = NA),
#    legend.position = "none",
   legend.title = element_text(size = 14, face = "bold"),
   legend.position = "bottom",
   legend.title.align = 0.5,
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text.x = element_blank(),
    axis.title.x = element_blank()) +
  guides(fill = guide_legend(title = "Land Use", 
                             title.position = "top",
                             nrow = 3))
ggsave(here("Graphics", "4_lu_county.jpg"), lu_county_plot)

lu_county_plot

```


### Projected Land Use change

```{r}
#---------------------------------------
# Projected Land use by land use type and county
#---------------------------------------
lu_change <- LU_change_raw %>% 
  clean_names() %>% 
  select(county, ir_25_55:wlf_25_55, mo_25_55:pas_25_55) %>% 
  pivot_longer(!county, names_to = "land_use", values_to = "acres") %>% 
    mutate(full_name = case_when(
    land_use == "ir_25_55" ~ "Impervious Roads",
    land_use == "inr_25_55" ~ "Impervious Non-Roads",
    land_use == "tci_25_55" ~ "Tree Canopy Over Impervious",
    land_use == "tg_25_55" ~ "Turf Grass",
    land_use == "tct_25_55" ~ "Tree Canopy over Turf Grass",
    land_use == "fore_25_55" ~ "Forest",
    land_use == "wlo_25_55" ~ "Wetlands (Other)",
    land_use == "wlf_25_55" ~ "Wetlands (Floodplain)",
    land_use == "wlt_25_55" ~ "Wetlands (Tidal)",
#    land_use == "wat_25_55" ~ "Water",
    land_use == "mo_25_55" ~ "Mixed Open",
    land_use == "crp_25_55" ~ "Cropland",
    land_use == "pas_25_55" ~ "Pasture",
  )) %>% 
  mutate(ounty = as.factor(county))

# Use stringr::str_wrap() to create breaks in long facet titles
stwr <- function(string, nwrap = 20){
  paste(strwrap(string, width = nwrap), collapse = "\n")
}

stwr = Vectorize(stwr)

lu_change$full_name = stwr(lu_change$full_name)

# Plot

lu_change_plot <- ggplot(lu_change, aes(x = fct_rev(county), y = acres)) +
  geom_col(aes(fill = county)) +
  scale_fill_manual(values = county_pallette) +
  facet_wrap(~full_name, scales = "free_y") +
  labs(x = "County", y = "Acres") +
  theme_minimal() +
   geom_hline(aes(yintercept=0)) +
  theme(
    text = element_text(family = "Times"),
    strip.background = element_rect(color = "grey40", fill = "grey30"),
    strip.text = element_text(color = "white", face = "bold"),
    panel.border = element_rect(color = "grey40", fill = NA),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    legend.title = element_text(size = 14, face = "bold"),
    legend.position = "bottom",
    legend.title.align = 0.5) +
  guides(fill = guide_legend(title = "County", 
                             title.position = "top",
                             nrow = 4))

lu_change_plot

# ggsave(here("Graphics", "4_lu_change.jpg"), lu_change_plot, width = 7, height = 7, dpi = "print")

```

### Tree canopy change inside and outside forest
```{r}
#---------------------------------------
# Inside/Outside Tree Canopy Forest Change
#---------------------------------------

# Clean and caluclate net change for each zone in and out of forest
in_out_forest_change <- zoning_raw %>% 
  select(genzone, tc_inside_forest_change_acres, tc_outside_forest_change_acres) %>% 
  pivot_longer(!genzone, names_to = "in_or_out", values_to = "acres_change") %>% 
  group_by(genzone, in_or_out) %>%
  summarize(tc_acres = sum(acres_change)) %>% 
  mutate(in_or_out = case_when(
    in_or_out == "tc_inside_forest_change_acres" ~ "Forest",
    in_or_out == "tc_outside_forest_change_acres" ~ "Tree Canopy Outside Forest"
  )) %>% 
  mutate(genzone = as.factor(genzone)) %>%
  mutate(genzone = fct_relevel(genzone,
            "Very Low Density Residential", "Low Density Residential", "Medium Density Residential", "High Density Residential", "Rural Low Density Residential", "Rural Medium Density Residential", "Rural High Density Residential", "Industrial", "Commercial", "Mixed Use", "Other"))

# Use stwr function created above to create line breaks in zone names
# Works but takes away order of zones
# in_out_forest_change$genzone = stwr(in_out_forest_change$genzone)

# Plot
#---------------------------------------
in_out_forest_plot <- ggplot(data = in_out_forest_change, aes(x = genzone, y = tc_acres)) +
  geom_col(position = "dodge", 
           aes(fill = in_or_out)) +
  labs(
    title = "Change in Tree Canopy Area by Zone Type",
#    x = "Zone Type",
    y = "Change in Area (Acres)") +
  scale_fill_manual(values = c("#24693d", # Inside
                               "#6eb663" # Outside
                               )) +
  coord_flip() +
  theme_minimal() +
  geom_hline(aes(yintercept=0)) +
  theme(
    text = element_text(family = "Times", size = 12),
    axis.text = element_text(size = 12),
    axis.title.x = element_text(size = 14, family = "Times", face = "bold"),
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold")
#    axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))
  )

in_out_forest_plot

ggsave(here("Graphics","4_in_out_forest_change.jpg"), in_out_forest_plot, width = 9.5, height = 7)

```

### General Zoning

```{r}
#---------------------------------------
# Forest change by general zoning
#---------------------------------------
zone_change <- zoning_raw %>% 
  select(genzone, zoning, tc_area_acres_change:impervious_area_acres_change) %>%
  pivot_longer(!genzone:zoning, names_to = "lc", values_to = "acres_change") %>%
  group_by(genzone, lc) %>%
  summarize(tc_acres = sum(acres_change)) %>% 
  mutate(genzone = as.factor(genzone)) %>%
  mutate(genzone = fct_relevel(genzone,
            "Very Low Density Residential", "Low Density Residential", "Medium Density Residential", "High Density Residential", "Rural Low Density Residential", "Rural Medium Density Residential", "Rural High Density Residential", "Industrial", "Commercial", "Mixed Use", "Other")) %>% 
    mutate(full_name = case_when(
    lc == "tc_area_acres_change" ~ "Tree Canopy Change",
    lc == "barren_area_acres_change" ~ "Barren Areas",
    lc == "buildings_area_acres_change" ~ "Building Areas",
    lc == "impervious_area_acres_change" ~ "Impervious Areas",
    lc == "low_veg_area_acres_change" ~ "Low Vegetation Areas",
    lc == "road_area_acres_change" ~ "Road Areas",
    lc == "shrub_area_acres_change" ~ "Shrub Areas",
    lc == "water_area_acres_change" ~ "Water Areas",
    lc == "wetlands_area_acres_change" ~ "Wetland Areas",
  )) %>% 
  mutate(full_name = as.factor(full_name)) %>% 
  mutate(full_name = fct_relevel(full_name, "Total Change", "Barren Areas", "Building Areas", "Impervious Areas", "Low Vegetation Areas", "Road Areas", "Shrub Areas", "Water Areas", "Wetland Areas"))

# "tc_area_acres_change", "barren_area_acres_change", "buildings_area_acres_change", "impervious_area_acres_change", "low_veg_area_acres_change", "road_area_acres_change", "shrub_area_acres_change", "water_area_acres_change", "wetlands_area_acres_change"

zone_change$full_name = stwr(zone_change$full_name)
  

# Facet by land cover
#---------------------------------------
zone_change_all <- ggplot(data = zone_change, aes(x = genzone, y = tc_acres)) +
  geom_col(aes(fill = genzone)) +
  facet_wrap(~full_name, scales = "free") +
  labs(
#    title = "Total Area Change",
    x = "Zone",
    y = "Change in Area (Acres)") +
  scale_fill_manual(values = lc_pallette) +
  theme_minimal() +
  geom_hline(aes(yintercept=0)) +
  theme(
#  legend.position = "none",
  legend.title = element_text(size = 16, face = "bold"),
   text = element_text(family = "Times"),
   axis.text.x = element_blank(),
   axis.title.x = element_blank(),
   axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0), size = 13, face = "bold"),
strip.background = element_rect(color = "grey40", fill = "grey30"),
strip.text = element_text(size = 8.5, color = "white", face = "bold"),
panel.border = element_rect(color = "grey40", fill = NA),
  ) +
  guides(fill = guide_legend(title = "Zone Type"))

zone_change_all

ggsave(here("Graphics","4_zone_change_panel.jpg"),zone_change_all, width = 8, height = 5.5)

```

### Sewer Service

Acres
```{r}
#---------------------------------------
# Sewer Service Area Change in Acres
#---------------------------------------

sewer_acres <- sewer_service %>% 
  select(genz_swr, tc_change_acres:impervious_change_acres) %>% 
  pivot_longer(!genz_swr, names_to = "type", values_to = "acres") %>% 
  group_by(genz_swr, type) %>% 
  summarize(acres_change = sum(acres)) %>% 
  drop_na() %>%  # Drop blank genz_swr (check eith Emma)
      mutate(type = case_when(
    type == "low_veg_change_acres" ~ "Low Vegetation",
    type == "barren_change_acres" ~ "Barren",
    type == "water_change_acres" ~ "Water",
    type == "buildings_change_acres" ~ "Buildings",
    type == "road_change_acres" ~ "Roads",
    type == "shrub_change_acres" ~ "Shrub",
    type == "wetlands_change_acres" ~ "Wetland",
    type == "impervious_change_acres" ~ "Impervious",
    type == "forest_change_acres" ~ "Forest",
    type == "tc_change_acres" ~ "Tree Canopy"))

# Use stringr function
sewer_acres$genz_swr = stwr(sewer_acres$genz_swr)
  
# Plot
#---------------------------------------
sewer_acres_plot <- ggplot(data = sewer_acres, aes(x = type, y = acres_change)) +
  geom_col(aes(fill = type)) +
  labs(title = "Land Cover Change 2013 to 2018 by Sewer Service Type",
       x = "Land Cover Type",
       y = "Change in Area (Acres)") +
  facet_wrap(~ genz_swr, scales = "free_y") +
  scale_fill_manual(values = lu_pallette) +
  theme_minimal() +
  geom_hline(aes(yintercept=0)) +
    theme(
  plot.title = element_text(size = 16, face = "bold"),
  legend.position = "bottom",
  legend.title.align = 0.5,
  legend.title = element_text(size = 14, face = "bold"),
#   text = element_text(family = "Times"),
   axis.text.x = element_blank(),
   axis.title.x = element_blank(),
   axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0), size = 14, face = "bold"),
strip.background = element_rect(color = "grey40", fill = "grey30"),
strip.text = element_text(size = 10, color = "white", face = "bold"),
panel.border = element_rect(color = "grey40", fill = NA),
  ) +
  guides(fill = guide_legend(title = "Land Cover Type",
                             title.position = "top"))

sewer_acres_plot

ggsave(here("Graphics", "4_sewer_service_acres.jpg"), sewer_acres_plot)

```
Sewer Service Area Forest Change
```{r}
#---------------------------------------
# Forest Change by Sewer Service Area
#---------------------------------------
sewer_forest_change <- sewer_service %>% 
  select(genz_swr, forest_change_acres:outside_forest_change_acres) %>% 
  pivot_longer(!genz_swr, names_to = "forest_type", values_to = "acres") %>% 
  group_by(genz_swr, forest_type) %>% 
  summarize(acres_change = sum(acres)) %>% 
  drop_na() %>% 
  mutate(forest_type = case_when(
    forest_type == "forest_change_acres" ~ "Forest",
    forest_type == "outside_forest_change_acres" ~ "Tree Canopy Outside Forest"))

# Use stringr function
sewer_forest_change$genz_swr = stwr(sewer_forest_change$genz_swr)

# Plot
#---------------------------------------
sewer_forest_plot <- ggplot(data = sewer_forest_change, aes(x = forest_type, y = acres_change)) +
  geom_col(position = "dodge", aes(fill = forest_type)) +
  labs(title = "Tree Canopy Change by Sewer Service Area",
       y = "Change in Area (Acres)") +
  facet_wrap(~genz_swr, scales = "free_y") +
  scale_fill_manual(values = c("#24693d", # Inside
                               "#6eb663" # Outside
                               )) +
  theme_minimal() +
  geom_hline(aes(yintercept=0)) +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.title = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 16, face = "bold"),
    legend.title = element_text(size = 14, face = "bold"),
    legend.title.align = 0.5,
    legend.position = "bottom",
    strip.background = element_rect(color = "grey40", fill = "grey30"),
    strip.text = element_text(size = 12, color = "white", face = "bold"),
    panel.border = element_rect(color = "grey40", fill = NA)
  ) +
  guides(fill = guide_legend(title = "Forest Type",
                               title.position = "top"))

sewer_forest_plot


ggsave(here("Graphics", "4_sewer_forest_change.jpg"), sewer_forest_plot)

```


### Loop Attempt

Notes from Jacob

data = whatever

cf_list <- unique(data$county_name)

for(cf_i in 1:cf_list) {
    temp_data <- data[which(data$county_name==cf_list[cf_i])]
    co_name = cf_list[cf_i]
    outfilename = paste0("C:/somefolder/subfolder/",co_name,"_specificplot.png") 
    ggplot()
    ggsave(
    outfilename,
    plot = last_plot(),
    device = NULL,
    path = NULL,
    scale = 1,
    width = NA,
    height = NA,
    units = c("in", "cm", "mm", "px"),
    dpi = 300,
    limitsize = TRUE,
    bg = NULL,
    ...
    )
    
```{r}

#---------------------------------------
# Attempted Looping onProjected Land use by land use type and county
#---------------------------------------

cf_list <- unique(lu_update$cntyname)

for(cf_i in 1:cf_list) {
    temp_data <- lu_update[which(lu_update$cntyname==cf_list[cf_i])]
    co_name = cf_list[cf_i]
    outfilename = paste0("C:\\Users\\mbouf\\Documents\\UVM\\Maryland_Technical_Forest\\MD_Forest\\Graphics\\LU_County_Loops",co_name,"_lu_plot.png") 
    ggplot(lu_update, aes(x = cntyname, y = acres)) +
  geom_col(aes(fill = cntyname)) +
  scale_fill_manual(values = county_pallette) +
  facet_wrap(~full_name, scales = "free_y") +
  labs(x = "County", y = "Acres") +
  theme_minimal() +
   geom_hline(aes(yintercept=0)) +
  theme(
    text = element_text(family = "Times"),
    strip.background = element_rect(color = "grey40", fill = "grey30"),
    strip.text = element_text(color = "white", face = "bold"),
    panel.border = element_rect(color = "grey40", fill = NA),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    legend.title = element_text(size = 14, face = "bold"),
    legend.position = "bottom",
    legend.title.align = 0.5) +
  guides(fill = guide_legend(title = "County", 
                             title.position = "top",
                             nrow = 4))
    ggsave(
    outfilename,
    plot = last_plot(),
    path = here("Graphics", "LU_County_Loops"),
    dpi = 300
    )}


```

Individually

```{r}

# Total Change
tc_change <- zone_change %>% 
  filter(lc == "tc_area_acres_change")

tc_change_plot <- ggplot(data = tc_change, aes(x = genzone, y = tc_acres)) +
  geom_col(aes(fill = genzone)) +
  labs(x = "Zone",
       y = "Acres",
       title = "Total Area Change") +
  coord_flip() +
  theme_minimal() +
  geom_hline(aes(yintercept=0)) +
  theme(
    legend.position = "none"
  )

ggsave(here("Graphics", "4_zone_change", "tc_change.jpg"), tc_change_plot)

# Wetlands Area Change
wetland_change <- zone_change %>% 
  filter(lc == "wetlands_area_acres_change")

wetland_change_plot <- ggplot(data = wetland_change, aes(x = genzone, y = tc_acres)) +
  geom_col(aes(fill = genzone)) +
  labs(x = "Zone",
       y = "Acres",
       title = "Wetlands Area Change") +
  coord_flip() +
  theme_minimal() +
  geom_hline(aes(yintercept=0)) +
  theme(
    legend.position = "none"
  )

ggsave(here("Graphics", "4_zone_change", "wetland_change.jpg"), wetland_change_plot)

# Water Area Change
water_change <- zone_change %>% 
  filter(lc == "water_area_acres_change")

water_change_plot <- ggplot(data = water_change, aes(x = genzone, y = tc_acres)) +
  geom_col(aes(fill = genzone)) +
  labs(x = "Zone",
       y = "Acres",
       title = "Water Area Change") +
  coord_flip() +
  theme_minimal() +
  geom_hline(aes(yintercept=0)) +
  theme(
    legend.position = "none"
  )

ggsave(here("Graphics", "4_zone_change", "water_change.jpg"), water_change_plot)

# Shrub Area Change
shrub_change <- zone_change %>% 
  filter(lc == "shrub_area_acres_change")

shrub_change_plot <- ggplot(data = shrub_change, aes(x = genzone, y = tc_acres)) +
  geom_col(aes(fill = genzone)) +
  labs(x = "Zone",
       y = "Acres",
       title = "Shrub Area Change") +
  coord_flip() +
  theme_minimal() +
  geom_hline(aes(yintercept=0)) +
  theme(
    legend.position = "none"
  )

ggsave(here("Graphics", "4_zone_change", "shrub_change.jpg"), shrub_change_plot)

# Road Area Change
road_change <- zone_change %>% 
  filter(lc == "road_area_acres_change")

road_change_plot <- ggplot(data = road_change, aes(x = genzone, y = tc_acres)) +
  geom_col(aes(fill = genzone)) +
  labs(x = "Zone",
       y = "Acres",
       title = "Road Area Change") +
  coord_flip() +
  theme_minimal() +
  geom_hline(aes(yintercept=0)) +
  theme(
    legend.position = "none"
  )

ggsave(here("Graphics", "4_zone_change", "road_change.jpg"), road_change_plot)

# Low Vegetation Area Change
low_veg_change <- zone_change %>% 
  filter(lc == "low_veg_area_acres_change")

low_veg_change_plot <- ggplot(data = low_veg_change, aes(x = genzone, y = tc_acres)) +
  geom_col(aes(fill = genzone)) +
  labs(x = "Zone",
       y = "Acres",
       title = "Low Vegetation Area Change") +
  coord_flip() +
  theme_minimal() +
  geom_hline(aes(yintercept=0)) +
  theme(
    legend.position = "none"
  )

ggsave(here("Graphics", "4_zone_change", "low_veg_change.jpg"), low_veg_change_plot)

# Impervious Area Change
impervious_change <- zone_change %>% 
  filter(lc == "impervious_area_acres_change")

impervious_change_plot <- ggplot(data = impervious_change, aes(x = genzone, y = tc_acres)) +
  geom_col(aes(fill = genzone)) +
  labs(x = "Zone",
       y = "Acres",
       title = "Impervious Area Change") +
  coord_flip() +
  theme_minimal() +
  geom_hline(aes(yintercept=0)) +
  theme(
    legend.position = "none"
  )

ggsave(here("Graphics", "4_zone_change", "impervious_change.jpg"), impervious_change_plot)

# Building Area Change
building_change <- zone_change %>% 
  filter(lc == "buildings_area_acres_change")

building_change_plot <- ggplot(data = building_change, aes(x = genzone, y = tc_acres)) +
  geom_col(aes(fill = genzone)) +
  labs(x = "Zone",
       y = "Acres",
       title = "Building Area Change") +
  coord_flip() +
  theme_minimal() +
  geom_hline(aes(yintercept=0)) +
  theme(
    legend.position = "none"
  )

ggsave(here("Graphics", "4_zone_change", "building_change.jpg"), building_change_plot)

# Barren Area Change
barren_change <- zone_change %>% 
  filter(lc == "barren_area_acres_change")

barren_change_plot <- ggplot(data = barren_change, aes(x = genzone, y = tc_acres)) +
  geom_col(aes(fill = genzone)) +
  labs(x = "Zone",
       y = "Acres",
       title = "Barren Area Change") +
  coord_flip() +
  theme_minimal() +
  geom_hline(aes(yintercept=0)) +
  theme(
    legend.position = "none"
  )

ggsave(here("Graphics", "4_zone_change", "barren_change.jpg"), barren_change_plot)



```

